---
title: "Main analyses E1. Language processing reveals conceptual combination in preverbal infants"
author: "BP"
output: html_document
---

```{r}
library(readxl)
library(tidyverse)
library(ggpubr)
library(rstatix)
library(scales)
library(lsr)
```

# DATA

Path, load the data.
```{r}
home_dir <- Sys.getenv("HOME")
path <- file.path(home_dir, "Documents", "GitHub", "composition", "data")
setwd(path) # Set the path
load("dataattendteste1.RData") # Load the raw data
```

# RESULTS

```{r}
# Compute ptl, corrptl
results <- d %>%
  group_by(ID,trial,phase,targetnumeral,atttrial) %>%
  summarise(tg = sum(tghit,na.rm=T),
            dt = sum(dthit,na.rm=T),
            ct = sum(centerhit,na.rm=T),
            ptl = tg/(tg+dt)) %>%
  select(ID,trial,phase,targetnumeral,ptl,atttrial) %>%
  pivot_wider(names_from=phase,values_from=ptl) %>%
  mutate(corrptl=test-pretest)
```

# STATS

## Descriptive

### Individual means

```{r}
# Compute individual means
resultsindm <- results %>%
  filter(atttrial != 0) %>%
  group_by(ID) %>%
  summarise(mpre=mean(pretest,na.rm=T),mtest = mean(test,na.rm=T), mcorrptl = mean(corrptl,na.rm=T),n()) 
```

```{r}
# Compute individual means
resultsindmnum <- results %>%
  filter(atttrial != 0) %>%
  group_by(ID,targetnumeral) %>%
  summarise(mpre=mean(pretest,na.rm=T),mtest = mean(test,na.rm=T), mcorrptl = mean(corrptl,na.rm=T),n()) 
```

### Group means

#### Overall

```{r}
resultsindm %>% # all participants
  summarise(gmpre=mean(mpre),gmtest = mean(mtest), gmcorrptl = mean(mcorrptl,na.rm=T),n())

resultsindm %>%
  get_summary_stats(mcorrptl,type="mean_sd")
```

#### By quantity label

```{r}
resultsindmnum %>%
  group_by(targetnumeral) %>%
  get_summary_stats(mcorrptl,type="mean_sd")
```


## Normality

```{r}
shapiro.test(resultsindm$mcorrptl)
```

## Main inferential

```{r}
t.test(resultsindm$mcorrptl, mu = 0, alternative = "two.sided")
cohensD(resultsindm$mcorrptl, mu = 0)
```

### Binomial

```{r}
binom.test(15,20, p = 0.5, alternative = "two.sided", conf.level = 0.95)
```

## Exploratory

Test wheter corrpl_target differes acress qunatity labeles (single vs. pair).

```{r}
t.test(data = resultsindmnum, mcorrptl~targetnumeral, paired= T,alternative = "two.sided")
cohensD(data = resultsindmnum, mcorrptl~targetnumeral)
```


Test whether PTL differs from chance at pretest, test.

```{r}
t.test(resultsindm$mpre, mu = 0.5, alternative = "two.sided")
t.test(resultsindm$mtest, mu = 0.5, alternative = "two.sided")
```

# PLOTS

```{r}
cbp1 <- c("#CC79A7", "gray80", "#0072B2", "#999999",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

cbp2 <- c("#CC79A7", "#E69F00", "#0072B2", "#F0E442",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

## Boxplots

ggplot(aes(x=as.factor(aoi),y=corr,fill=aoi,color = aoi)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 0, size = .5, lty = "longdash", color = "gray") +
  geom_boxplot(outlier.shape = NA, alpha = 1, width = .5, color = "black", size = .15) +
  geom_point(size = .75, alpha = .55, position = position_jitter(seed = 1, width = .1), color = "black") +
  ylim(-.56,.56) +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point", color = "white", 
               size = 2, shape = "circle") +
  #labs(title = "Experiment 2", subtitle = "Composition test") +
  scale_colour_manual(values=cbp2) +
  scale_fill_manual(values=cbp2) 

### Overall

```{r}
resultsindm %>%
  ggplot(aes(x=1,y=mcorrptl)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 0, size = .5, lty = "longdash", color = "gray") +
  geom_boxplot(outlier.shape = NA, alpha = 1, width = .165,
               color="gray10",size =.35, fill = "#CC79A7") +
  geom_point(size = .75, alpha = .55, position = position_jitter(seed = 1, width = .175), color = "black") +
  ylim(-.56,.56) +
  ylab("Mean Baseline-Corrected Proportion of Looking") +
  xlim(0,2) +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point", color = "white", 
               size = 2, shape = "circle") 
  #labs(title = "Experiment 1", subtitle = "Generalization test") 

overall
```
```{r}
setwd(pathplots) 
  ggsave("boxe1.png", plot = last_plot(), width = 7.5, height = 7.5, units = c("cm"))
```

### Single

```{r}
a <- resultsindmnum %>%
  filter(targetnumeral == "single") %>%
  ggplot(aes(x=1,y=mcorrptl)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 18),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 20),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 0, size = .5, lty = "longdash", color = "gray") +
  geom_boxplot(outlier.shape = NA, alpha = .35, width = .55,
               color="gray10",size =.25, fill = "#CC79A7") +
  geom_jitter(position=position_jitter(.65), size = .25, color = "black") +
  ylim(-.56,.56) +
  xlim(0,2) +
  ggtitle("One")
```

### Pair

```{r}
b <- resultsindmnum %>%
  filter(targetnumeral == "pair") %>%
  ggplot(aes(x=1,y=mcorrptl)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 18),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12, color = "white"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 0, size = .5, lty = "longdash", color = "gray") +
  geom_boxplot(outlier.shape = NA, alpha = .35, width = .55,
               color="gray10",size =.25, fill = "#CC79A7") +
  geom_jitter(position=position_jitter(.75), size = .25, color = "black") +
  ylim(-.56,.56) +
  #ylab("Mean Baseline-Corrected Proportion of Looking") +
  xlim(0,2) +
  ggtitle("Two")

b
```


```{r}
ggarrange(a,b,nrow = 1)

```


```{r}
setwd(pathplots) 
  ggsave("boxe1Num.png", plot = last_plot(), width = 8, height = 8, units = c("cm"))
```

###Combine plots

```{r}
side <- ggarrange(a,b,ncol=1)
  ggarrange(overall,side, nrow = 1, widths = c(2.5,1.325))
```

```{r}
setwd("~/Documents/GitHub/composition/plots/") # Set the path
ggsave("boxe1_combined.png", plot = last_plot(), width = 10, height = 10, units = c("cm"))
```


## Time-course plots

```{r}
dctime <- merge(d,results,by=c("ID","trial","targetnumeral","atttrial"))
```

```{r}
dctime %>%
  filter(atttrial == 1) %>%
  mutate(ptg = tghit/(tghit+dthit)) %>%
  mutate(corrtg = ptg-pretest) %>%
  group_by(ID,phase,sample) %>%
  summarise(tcorrptl = mean(corrtg,na.rm=T)) %>%
  group_by(phase,sample) %>%
  summarise(tcorrtg = mean(tcorrptl,na.rm=T)) %>%
  gather(key="aoi",value = "corr",c("tcorrtg")) %>%
  ggplot(aes(x=sample,y=corr,color=aoi)) +
  geom_line() +
  ylim(-.5,.5) +
  facet_wrap(phase ~ .)
```

Baseline-corrected plots.

```{r}
aux <- dctime %>%
  ungroup() %>%
  filter(atttrial == 1) %>%
  filter(phase == "test")

l = nrow(aux)

auxctime <- dctime %>%
  filter(atttrial == 1) %>%
  filter(phase == "test")%>%
  mutate(samplegroup = rep(1:130,each=3,l/390))%>%
  mutate(sumaoi=tghit+dthit) %>%
  mutate(ptg = tghit/sumaoi) %>%
  mutate(corrtg = ptg-pretest) %>%
  group_by(ID,samplegroup) %>%
  summarise(tcorrptl = mean(corrtg,na.rm=T)) %>%
  group_by(samplegroup) %>%
  get_summary_stats(tcorrptl, type="mean_se")
```

```{r}
auxctime %>%
  ggplot(aes(x=samplegroup,y=mean,color="#CC79A7",fill="#CC79A7")) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_blank()) +
  geom_vline(xintercept = 30, size=.15, color="black") +
  geom_vline(xintercept = 240/390*130, size=.15, color="black") +
  geom_hline(yintercept = 0, size=.15, color="black") +
  geom_ribbon(aes(ymin = mean-se, ymax = mean+se),alpha=.15, size = 0) +
  geom_line(size=.75) +
  ylim(-.56,.56) +
  xlab("Time (seconds)") +
  scale_x_continuous(
    breaks = c(1,61/390*130,121/390*130,181/390*130,241/390*130,301/390*130,360/390*130),
                     labels = c("0","1", "2", "3", "4", "5","6")) +
  scale_colour_manual(values=cbp2) +
  scale_fill_manual(values=cbp2)
```

```{r warning=FALSE}
setwd("~/Documents/GitHub/composition/plots/") # Set the path
ggsave("timee1.png", plot = last_plot(), width = 15, height = 10, units = c("cm"))
```

# REVISION

## pt

```{r}
results %>%
  filter(atttrial != 0) %>%
  group_by(ID) %>%
  summarise(mpretest = mean(pretest, na.rm = T),
            mtest = mean(test, na.rm = T)) %>%
  ungroup() %>%
  summarise(mpretest = mean(mpretest, na.rm = T),
            mtest = mean(mtest, na.rm = T)) %>%
  mutate(mtest-mpretest)
```


```{r}
e1p <- results %>%
  filter(atttrial != 0) %>%
  group_by(ID) %>%
  summarise(mpretest = mean(pretest, na.rm = T),
            mtest = mean(test, na.rm = T)) %>%
  gather(key = "phase", value = "value", c("mpretest","mtest")) %>%
  ggplot(aes(x = as.factor(phase), y = value, color = "#CC79A7")) +
  theme_pubr() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 12.5),
        title = element_text(size = 10)) +
  geom_jitter(position=position_jitter(.15), size = .96, alpha = .25,color = "#CC79A7") +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point",
               color = "#CC79A7", 
               size = 2, shape = "circle",position=position_dodge(width = .75)) +
  stat_summary(fun.data = mean_cl_normal, na.rm = TRUE,
               color = "#CC79A7", 
               size = .5, position=position_dodge(width = .75),geom = "errorbar", width = 0) +  ylim(0,0.8)
```

## RAW LTimes

```{r}
resultsraw <- d %>%
  group_by(ID,trial,phase,atttrial) %>%
  summarise(sumtg = sum(tghit,na.rm=T)*1000/60/1000,
            sumdt = sum(dthit,na.rm=T)*1000/60/1000)%>%
  select(ID,trial,phase,sumtg,sumdt,atttrial) %>%
  filter(atttrial == 1) %>%
  group_by(ID,phase) %>%
  summarise(tg = mean(sumtg, na.rm=T),
            dt = mean(sumdt, na.rm=T)) %>%
  gather(key = "aoi", value = "value", c("tg","dt")) %>%
  mutate(aoi = factor(aoi, levels = c("tg","dt")))
  mutate(phase = recode(phase, "pretest" = "baseline", "test" = "response"))

View(resultsraw)
```

```{r}
e1b <- resultsraw %>%
  ggplot(aes(x = as.factor(phase), y = value, fill = aoi, color = aoi)) +
  theme_pubr() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 12.5),
        title = element_text(size = 18)) +
  geom_jitter(position=position_jitterdodge(.35), size = .96, alpha = .25) +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point",
               #color = "black", 
               size = 2, shape = "circle",position=position_dodge(width = .75)) +
  stat_summary(fun.data = mean_cl_normal, na.rm = TRUE,
               #color = "black", 
               size = .5, position=position_dodge(width = .75),geom = "errorbar", width = 0) +
  scale_color_manual(values=cbp1) +
  scale_fill_manual(values=cbp1) +
  ylim(0,3.15) +
  ggtitle("Experiment 1")
```


```{r}
ggarrange(e1b, e1p, ncol = 1)
```


```{r}
setwd(pathplots)
ggsave("pl1.png", plot = last_plot(), width = 5.5, height = 15, units = c("cm"))
```

### by Number

```{r}
resultsrawnumber <- d %>%
  group_by(ID,trial,phase,targetnumeral,attpretest,atttest,atttrial) %>%
  summarise(sumtg = sum(tghit,na.rm=T)*1000/60/1000)%>%
  select(ID,trial,phase,targetnumeral,sumtg,
         attpretest,atttest,atttrial) %>%
  group_by(ID,phase,targetnumeral) %>%
  summarise(value = mean(sumtg, na.rm=T))

View(resultsrawnumber)
```

```{r}
e1rc <- resultsrawnumber %>%
  ggplot(aes(x = as.factor(phase), y = value, fill = targetnumeral, color = targetnumeral)) +
  theme_pubr() +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text = element_text(size = 12)) +
  geom_jitter(position=position_jitterdodge(.2), size = .96, alpha = .65) +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point",
               color = "black", 
               size = 2, shape = "circle",position=position_dodge(width = .75)) +
  stat_summary(fun.data = mean_cl_normal, na.rm = TRUE,
               color = "black", 
               size = .5, position=position_dodge(width = .75),geom = "errorbar", width = 0) +
  scale_color_manual(values=c("red3","purple")) +
  ylim(0,3.15) + 
  ggtitle("Experiment 1")
```

# SAVE

```{r}
setwd("~/Documents/GitHub/composition/results/") # Set the path
save(resultsindm,resultsindmnum, file = "resultse1.RData")
```