---
title: "Main analyses E2-3. Language processing reveals conceptual combination in preverbal infants"
author: "BP"
output: html_document
---

```{r}
library(readxl)
library(tidyverse)
library(ggpubr)
library(rstatix)
library(scales)
library(lsr)
library(ggdist)
library(tidyquant)
library(gghalves)
```

# DATA

Paths.

```{r warning=FALSE}
home_dir <- Sys.getenv("HOME") #("USERPROFILE")
path <- file.path(home_dir, "Documents", "GitHub", "composition", "data")
pathresults <- file.path(home_dir, "Documents", "GitHub", "composition", "results")
pathplots <- file.path(home_dir, "Documents", "GitHub", "composition", "plots")
```

Load composition data from E2, E3.

```{r}
setwd(path) # Set the path
load("dataattendteste2e3.RData") # Load the raw data
```

```{r}
dcompose <- dcompose %>%
  filter(ifelse(experiment == "Experiment 2", !ID %in% c(2,10), !ID %in% c(3,7))) 
```

Load kind-recognition results.
```{r}
setwd(pathresults) 
load("resultskindrecognition.RData") 
```

# RESULTS

Compute the proportion of looking at each AOI (target, number distractor, kind distractor, unrelated/mixed distractor).

```{r}
resultscompose <- dcompose %>%
  group_by(experiment,ID,trial,phase,targetnumeral,attpretest,atttest,atttrial) %>%
  summarise(tg = sum(tghit,na.rm=T),
            dtnum = sum(dtnumhit,na.rm=T),
            dtkind = sum(dtkindhit,na.rm=T),
            dtunrel = sum(dtkunrelatedhit,na.rm=T),
            ct = sum(centerhit,na.rm=T),
            ptg = tg/(tg+dtnum+dtkind+dtunrel),
            pnum = dtnum/(tg+dtnum+dtkind+dtunrel),
            pkind = dtkind/(tg+dtnum+dtkind+dtunrel),
            punrel = dtunrel/(tg+dtnum+dtkind+dtunrel)) %>%
  select(ID,trial,phase,targetnumeral,ptg,pnum,pkind,punrel,attpretest,atttest,atttrial) %>%
  pivot_wider(names_from=phase,values_from=c("ptg","pnum","pkind","punrel")) %>%
  mutate(corrtg=ptg_test-ptg_pretest) %>%
  mutate(corrnum=pnum_test-pnum_pretest) %>%
  mutate(corrkind=pkind_test-pkind_pretest) %>%
  mutate(corrunrel=punrel_test-punrel_pretest)
```

```{r}
# Combine w/ kind info
resultscombined <- merge(resultscompose,resultskindindm,by=c("experiment","ID"))
```

# STATS

## Descriptive overall

### Individual means

```{r}
# Individual means ====
resultscombinedindm <- resultscombined %>%
  filter(atttrial != 0) %>%
  group_by(experiment,ID,kindknower,mcorrptl) %>%
  summarise(mpretg = mean(ptg_pretest,na.rm=T),
            mprenum = mean(pnum_pretest,na.rm=T),
            mprekind = mean(pkind_pretest,na.rm=T),
            mpreun = mean(punrel_pretest,na.rm=T),
            mtesttg = mean(ptg_test,na.rm=T),
            mtestnum = mean(pnum_test,na.rm=T),
            mtestkind = mean(pkind_test,na.rm=T),
            mtestun = mean(punrel_test,na.rm=T),
            mcorrtg = mean(corrtg,na.rm=T),
            mcorrnum = mean(corrnum,na.rm=T),
            mcorrkind = mean(corrkind,na.rm=T),
            mcorrun = mean(corrunrel,na.rm=T),
            n()) 
```

### Group means

```{r}
resultscombinedindm %>%
  gather(key="aoi",value="mcorr",c("mpretg","mprenum","mprekind","mpreun")) %>%
  filter(kindknower == 1) %>%
  group_by(experiment,aoi) %>%
  get_summary_stats(mcorr, type = "mean_se")

resultscombinedindm %>%
  gather(key="aoi",value="mcorr",c("mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  filter(kindknower == 1) %>%
  group_by(experiment,aoi) %>%
  get_summary_stats(mcorr, type = "mean_sd")
```


## Descriptive split by numeral

### Individual means

```{r}
# Individual means ====
resultscombinedindm_splitNumeral <- resultscombined %>%
  filter(atttrial != 0) %>%
  group_by(experiment,ID,kindknower,mcorrptl,targetnumeral) %>%
  summarise(mpretg = mean(ptg_pretest,na.rm=T),
            mprenum = mean(pnum_pretest,na.rm=T),
            mprekind = mean(pkind_pretest,na.rm=T),
            mpreun = mean(punrel_pretest,na.rm=T),
            mtesttg = mean(ptg_test,na.rm=T),
            mtestnum = mean(pnum_test,na.rm=T),
            mtestkind = mean(pkind_test,na.rm=T),
            mtestun = mean(punrel_test,na.rm=T),
            mcorrtg = mean(corrtg,na.rm=T),
            mcorrnum = mean(corrnum,na.rm=T),
            mcorrkind = mean(corrkind,na.rm=T),
            mcorrun = mean(corrunrel,na.rm=T),
            n()) 
```

### Group means

```{r}
resultscombinedindm_splitNumeral %>%
  gather(key="aoi",value="mcorr",c("mpretg","mprenum","mprekind","mpreun")) %>%
  filter(kindknower == 1) %>%
  group_by(experiment,aoi,targetnumeral) %>%
  get_summary_stats(mcorr, type = "mean_se")

resultscombinedindm_splitNumeral %>%
  gather(key="aoi",value="mcorr",c("mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  filter(kindknower == 1) %>%
  group_by(experiment,aoi,targetnumeral) %>%
  get_summary_stats(mcorr, type = "mean_sd")
```

## Normality

```{r}
aux = resultscombinedindm %>%filter(kindknower==1)
```

### E2

```{r}
shapiro.test(aux$mcorrtg[aux$experiment=="Experiment 2"])
shapiro.test(aux$mcorrnum[aux$experiment=="Experiment 2"])
shapiro.test(aux$mcorrkind[aux$experiment=="Experiment 2"])
shapiro.test(aux$mcorrun[aux$experiment=="Experiment 2"])
```

### E3

```{r}
shapiro.test(aux$mcorrtg[aux$experiment=="Experiment 3"])
shapiro.test(aux$mcorrnum[aux$experiment=="Experiment 3"])
shapiro.test(aux$mcorrkind[aux$experiment=="Experiment 3"])
shapiro.test(aux$mcorrun[aux$experiment=="Experiment 3"])
```

## Main inferential

### E2

```{r}
t.test(aux$mcorrtg[aux$experiment=="Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(aux$mcorrtg[aux$experiment=="Experiment 2"], mu = 0)
t.test(aux$mcorrkind[aux$experiment=="Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(aux$mcorrkind[aux$experiment=="Experiment 2"], mu = 0)
t.test(aux$mcorrnum[aux$experiment=="Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(aux$mcorrnum[aux$experiment=="Experiment 2"], mu = 0)
t.test(aux$mcorrun[aux$experiment=="Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(aux$mcorrun[aux$experiment=="Experiment 2"], mu = 0)
```

```{r}
t.test(aux$mcorrtg[aux$experiment=="Experiment 2"], aux$mcorrkind[aux$experiment=="Experiment 2"], alternative = "two.sided",paired=T)
cohensD(aux$mcorrtg[aux$experiment=="Experiment 2"], aux$mcorrkind[aux$experiment=="Experiment 2"])
t.test(aux$mcorrtg[aux$experiment=="Experiment 2"], aux$mcorrnum[aux$experiment=="Experiment 2"], alternative = "two.sided",paired=T)
cohensD(aux$mcorrtg[aux$experiment=="Experiment 2"], aux$mcorrnum[aux$experiment=="Experiment 2"])
t.test(aux$mcorrtg[aux$experiment=="Experiment 2"], aux$mcorrun[aux$experiment=="Experiment 2"], alternative = "two.sided",paired=T)
cohensD(aux$mcorrtg[aux$experiment=="Experiment 2"], aux$mcorrun[aux$experiment=="Experiment 2"])
```

#### Multiple-comparison corrections

```{r}
e2tg <- aux$mcorrtg[aux$experiment=="Experiment 2"]
e2kind <- aux$mcorrkind[aux$experiment=="Experiment 2"]
e2num <- aux$mcorrnum[aux$experiment=="Experiment 2"]
e2unrel <- aux$mcorrun[aux$experiment=="Experiment 2"]
```

```{r}
multcomp <- aux %>% gather(key="aoi",value="corr",c("mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  filter(experiment == "Experiment 2") %>%
  convert_as_factor(aoi, ID) %>%
  select(experiment, ID,aoi,corr)

multcomp #%>% sample_n_by(experiment,aoi, size = 1)
```
```{r}
comparisons <- list(c("mcorrtg", "mcorrnum"), 
                    c("mcorrtg", "mcorrkind"), 
                    c("mcorrtg", "mcorrun"))
```


```{r}
stat.test <- multcomp %>%
  group_by(experiment) %>%
  pairwise_t_test(
    corr ~ aoi, paired = TRUE, 
    p.adjust.method = "holm",
    comparisons = comparisons
    ) #%>% select(-df, -statistic, -p) # Remove details
stat.test
```

### E3

```{r}
t.test(aux$mcorrtg[aux$experiment=="Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(aux$mcorrtg[aux$experiment=="Experiment 3"], mu = 0)
t.test(aux$mcorrnum[aux$experiment=="Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(aux$mcorrnum[aux$experiment=="Experiment 3"], mu = 0)
t.test(aux$mcorrkind[aux$experiment=="Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(aux$mcorrkind[aux$experiment=="Experiment 3"], mu = 0)
t.test(aux$mcorrun[aux$experiment=="Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(aux$mcorrun[aux$experiment=="Experiment 3"], mu = 0)
```


```{r}
t.test(aux$mcorrtg[aux$experiment=="Experiment 3"], aux$mcorrnum[aux$experiment=="Experiment 3"], alternative = "two.sided",paired=T)
cohensD(aux$mcorrtg[aux$experiment=="Experiment 3"], aux$mcorrnum[aux$experiment=="Experiment 3"])
t.test(aux$mcorrtg[aux$experiment=="Experiment 3"], aux$mcorrkind[aux$experiment=="Experiment 3"], alternative = "two.sided",paired=T)
cohensD(aux$mcorrtg[aux$experiment=="Experiment 3"], aux$mcorrkind[aux$experiment=="Experiment 3"])
t.test(aux$mcorrtg[aux$experiment=="Experiment 3"], aux$mcorrun[aux$experiment=="Experiment 3"], alternative = "two.sided",paired=T)
cohensD(aux$mcorrtg[aux$experiment=="Experiment 3"], aux$mcorrun[aux$experiment=="Experiment 3"])
```

### Binomial

Experiment 2.
```{r}
binom.test(16,20, p = 0.5, alternative = "two.sided", conf.level = 0.95)
```

Experiment 3.
```{r}
binom.test(15,20, p = 0.5, alternative = "two.sided", conf.level = 0.95)
```

## Exploratory

### All participants

```{r}
t.test(resultscombinedindm$mcorrtg[resultscombinedindm$experiment=="Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(resultscombinedindm$mcorrtg[resultscombinedindm$experiment=="Experiment 2"], mu = 0)
t.test(resultscombinedindm$mcorrkind[resultscombinedindm$experiment=="Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(resultscombinedindm$mcorrkind[resultscombinedindm$experiment=="Experiment 2"], mu = 0)
t.test(resultscombinedindm$mcorrnum[resultscombinedindm$experiment=="Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(resultscombinedindm$mcorrnum[resultscombinedindm$experiment=="Experiment 2"], mu = 0)
t.test(resultscombinedindm$mcorrun[resultscombinedindm$experiment=="Experiment 2"], mu = 0, alternative = "two.sided")
cohensD(resultscombinedindm$mcorrun[resultscombinedindm$experiment=="Experiment 2"], mu = 0)
```

```{r}
t.test(resultscombinedindm$mcorrtg[resultscombinedindm$experiment=="Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(resultscombinedindm$mcorrtg[resultscombinedindm$experiment=="Experiment 3"], mu = 0)
t.test(resultscombinedindm$mcorrkind[resultscombinedindm$experiment=="Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(resultscombinedindm$mcorrkind[resultscombinedindm$experiment=="Experiment 3"], mu = 0)
t.test(resultscombinedindm$mcorrnum[resultscombinedindm$experiment=="Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(resultscombinedindm$mcorrnum[resultscombinedindm$experiment=="Experiment 3"], mu = 0)
t.test(resultscombinedindm$mcorrun[resultscombinedindm$experiment=="Experiment 3"], mu = 0, alternative = "two.sided")
cohensD(resultscombinedindm$mcorrun[resultscombinedindm$experiment=="Experiment 3"], mu = 0)
```

### Baseline looking

Experiment 2.
```{r}
t.test(aux$mpretg[aux$experiment=="Experiment 2"], mu = .25, alternative = "two.sided")
t.test(aux$mprenum[aux$experiment=="Experiment 2"], mu = .25, alternative = "two.sided")
t.test(aux$mprekind[aux$experiment=="Experiment 2"], mu = .25, alternative = "two.sided")
t.test(aux$mpreun[aux$experiment=="Experiment 2"], mu = .25, alternative = "two.sided")
```

Experiment 3.
```{r}
t.test(aux$mpretg[aux$experiment=="Experiment 3"], mu = .25, alternative = "two.sided")
t.test(aux$mprenum[aux$experiment=="Experiment 3"], mu = .25, alternative = "two.sided")
t.test(aux$mprekind[aux$experiment=="Experiment 3"], mu = .25, alternative = "two.sided")
t.test(aux$mpreun[aux$experiment=="Experiment 3"], mu = .25, alternative = "two.sided")
```
```{r}
```

# PLOTS

```{r}
cbp1 <- c("#CC79A7", "#E69F00", "#0072B2", "#999999",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

cbp2 <- c("#009E73", "#E69F00", "#0072B2", "#999999",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```



## Boxplots

### E2

```{r}
resultscombinedindm %>%
  gather(key="aoi",value="corr",c("mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  mutate(aoi = recode(aoi,"mcorrtg" = "aTG","mcorrkind" = "dtkind","mcorrnum" = "dtnum")) %>%
  filter(kindknower == 1) %>%
  filter(experiment == "Experiment 2") %>%
  ggplot(aes(x=as.factor(aoi),y=corr,fill=aoi,color = aoi)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 0, size = .5, lty = "longdash", color = "gray") +
  geom_boxplot(outlier.shape = NA, alpha = 1, width = .35, color = "black", size = .15) +
  stat_halfeye(adjust = 1.5, justification = -.8, alpha = .2, width = .4, .width = 0, point_colour = NA) +
  #geom_half_point(
    ## draw jitter on the left side = "l", 
    ## control range of jitter range_scale = .35, 
    ## add some transparency alpha = .55) +
  geom_point(size = .75, alpha = .55, position = position_jitter(seed = 1, width = .1), color = "black") +
  #stat_dots(binwidth = .05) +
  #geom_violin(outlier.shape = NA, alpha = .75, width = .45, color="gray10",size =.35) +
  #geom_jitter(aes(color = aoi),position=position_jitter(.15), size = 1, alpha = .75) +
  ylim(-.56,.56) +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point", color = "white", 
               size = 2, shape = "circle") +
  labs(title = "Experiment 2", subtitle = "Composition test") +
  scale_colour_manual(values=cbp1) +
  scale_fill_manual(values=cbp1) 
```

```{r}
setwd(pathplots) 
ggsave("boxe2.png", plot = last_plot(), width = 10, height = 10, units = c("cm"))
```

Test.

```{r}
aux <- resultscombinedindm %>%
  mutate(targetnumeral = "overall") %>%
  rbind(resultscombined,resultscombinedindm_splitNumeral) %>%
  gather(key="aoi",value="corr",c("mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  mutate(aoi = recode(aoi,"mcorrtg" = "aTG","mcorrkind" = "dtkind","mcorrnum" = "dtnum")) %>%
  filter(kindknower == 1) %>%
  filter(experiment == "Experiment 2")
```

```{r}
resultscombinedindm %>%
  mutate(targetnumeral = "overall") %>%
  rbind(resultscombined,resultscombinedindm_splitNumeral) %>%
  gather(key="aoi",value="corr",c("mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  mutate(aoi = recode(aoi,"mcorrtg" = "aTG","mcorrkind" = "dtkind","mcorrnum" = "dtnum")) %>%
  filter(kindknower == 1) %>%
  filter(experiment == "Experiment 2") %>%
  ggplot(aes(x=as.factor(aoi),y=corr,fill=aoi,color = targetnumeral, alpha = targetnumeral)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 0, size = .5, lty = "longdash", color = "gray") +
  geom_boxplot(outlier.shape = NA, alpha = 1, width = .35, color = "black", size = .15) +
  #stat_halfeye(adjust = 1.5, justification = -.8, alpha = .2, width = .4, .width = 0, point_colour = NA) +
  #geom_half_point(
    ## draw jitter on the left side = "l", 
    ## control range of jitter range_scale = .35, 
    ## add some transparency alpha = .55) +
  geom_point(size = .75, alpha = .55, position = position_jitter(seed = 1, width = .1), color = "black") +
  #stat_dots(binwidth = .05) +
  #geom_violin(outlier.shape = NA, alpha = .75, width = .45, color="gray10",size =.35) +
  #geom_jitter(aes(color = aoi),position=position_jitter(.15), size = 1, alpha = .75) +
  ylim(-.56,.56) +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point", color = "white", 
               size = 2, shape = "circle") +
  labs(title = "Experiment 2", subtitle = "Composition test") +
  scale_colour_manual(values=cbp1) +
  scale_fill_manual(values=cbp1) 
```

#### Pair

```{r}
plotsingle <- resultscombinedindm_splitNumeral %>%
  filter(targetnumeral == "single") %>%
  filter(kindknower == 1) %>%
  filter(experiment == "Experiment 2") %>%
  gather(key="aoi",value="corr",c("mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  mutate(aoi = recode(aoi,"mcorrtg" = "aTG","mcorrkind" = "dtkind","mcorrnum" = "dtnum"))
```


```{r}
resultscombinedindm_splitNumeral %>%
  filter(targetnumeral == "single") %>%
  filter(kindknower == 1) %>%
  filter(experiment == "Experiment 2") %>%
  gather(key="aoi",value="corr",c("mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  mutate(aoi = recode(aoi,"mcorrtg" = "aTG","mcorrkind" = "dtkind","mcorrnum" = "dtnum")) %>%
  ggplot(aes(x=as.factor(aoi),y=corr,fill=aoi,color = aoi)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 0, size = .5, lty = "longdash", color = "gray") +
  geom_boxplot(outlier.shape = NA, alpha = 1, width = .35, color = "black", size = .15) +
  stat_halfeye(adjust = 1.5, justification = -.8, alpha = .2, width = .4, .width = 0, point_colour = NA) +
  #geom_half_point(
    ## draw jitter on the left side = "l", 
    ## control range of jitter range_scale = .35, 
    ## add some transparency alpha = .55) +
  geom_point(size = .75, alpha = .55, position = position_jitter(seed = 1, width = .1), color = "black") +
  #stat_dots(binwidth = .05) +
  #geom_violin(outlier.shape = NA, alpha = .75, width = .45, color="gray10",size =.35) +
  #geom_jitter(aes(color = aoi),position=position_jitter(.15), size = 1, alpha = .75) +
  ylim(-.56,.56) +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point", color = "white", 
               size = 2, shape = "circle") +
  labs(title = "Experiment 2", subtitle = "Composition test") +
  scale_colour_manual(values=cbp1) +
  scale_fill_manual(values=cbp1) 
```

```{r}
setwd(pathplots) 
ggsave("boxe2_single.png", plot = last_plot(), width = 10, height = 10, units = c("cm"))
```

### E3

```{r}
resultscombinedindm %>%
  gather(key="aoi",value="corr",c("mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  mutate(aoi = recode(aoi,"mcorrtg" = "aTG","mcorrkind" = "dtkind","mcorrnum" = "dtnum")) %>%
  filter(kindknower == 1) %>%
  filter(experiment == "Experiment 3") %>%
  ggplot(aes(x=as.factor(aoi),y=corr,fill=aoi)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 0, size = .5, lty = "longdash", color = "gray") +
  geom_boxplot(outlier.shape = NA, alpha = .5, width = .6, color="gray10",size =.35) +
  geom_jitter(aes(color = aoi),position=position_jitter(.15), size = .75) +
  ylim(-.56,.56) +
  #ylab("Mean Baseline-Corrected Proportion of Looking") +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point", color = "white", 
               size = 4, shape = "diamond") +
  labs(title = "Experiment 3", subtitle = "Composition test") +
  scale_colour_manual(values=cbp1) +
  scale_fill_manual(values=cbp1)
```

```{r}
setwd("~/Documents/GitHub/composition/plots/") # Set the path
ggsave("boxe3.png", plot = last_plot(), width = 10, height = 10, units = c("cm"))
```

## Time-course plots

```{r}
dctime <- merge(dcompose,resultscombined,by=c("experiment","ID","trial","targetnumeral","atttrial"))
```

```{r}
dctime %>%
  filter(atttrial == 1) %>%
  filter(experiment == "Experiment 2") %>%
  mutate(ptg = tghit/(tghit+dtnumhit+dtkindhit+dtkunrelatedhit)) %>%
  mutate(pnum = dtnumhit/(tghit+dtnumhit+dtkindhit+dtkunrelatedhit)) %>%
  mutate(pkind = dtkindhit/(tghit+dtnumhit+dtkindhit+dtkunrelatedhit)) %>%
  mutate(corrtg = ptg-ptg_pretest) %>%
  mutate(corrnum = pnum-pnum_pretest) %>%
  mutate(corrkind = pkind-pkind_pretest) %>%
  group_by(ID,phase,sample,kindknower) %>%
  summarise(tcorrptl = mean(corrtg,na.rm=T),
            tcorrn = mean(corrnum,na.rm=T),
            tcorrk = mean(corrkind,na.rm=T)) %>%
  group_by(phase,sample,kindknower) %>%
  summarise(tcorrtg = mean(tcorrptl,na.rm=T),
            tcorrn = mean(tcorrn,na.rm=T),
            tcorrk = mean(tcorrk,na.rm=T)) %>%
  gather(key="aoi",value = "corr",c("tcorrtg","tcorrn","tcorrk")) %>%
  ggplot(aes(x=sample,y=corr,color=aoi)) +
  geom_line() +
  ylim(-.5,.5) +
  facet_wrap(phase ~ kindknower)
```
Baseline-corrected plots.
```{r}
aux <- dctime %>%
  ungroup() %>%
  filter(atttrial == 1) %>%
  filter(phase == "test")

l = nrow(aux)

auxctime <- dctime %>%
  filter(atttrial == 1) %>%
  filter(phase == "test") %>%
  mutate(samplegroup = rep(1:130,each=3,l/390))%>%
  mutate(sumaoi=tghit+dtnumhit+dtkindhit+dtkunrelatedhit) %>%
  mutate(ptg = tghit/sumaoi) %>%
  mutate(pnum = dtnumhit/sumaoi) %>%
  mutate(pkind = dtkindhit/sumaoi) %>%
  mutate(punrel = dtkunrelatedhit/sumaoi) %>%
  mutate(corrtg = ptg-ptg_pretest) %>%
  mutate(corrnum = pnum-pnum_pretest) %>%
  mutate(corrkind = pkind-pkind_pretest) %>%
  mutate(corrunrel = punrel-punrel_pretest) %>%
  group_by(experiment,kindknower,ID,samplegroup) %>%
  summarise(tcorrptl = mean(corrtg,na.rm=T),
            tcorrn = mean(corrnum,na.rm=T),
            tcorrk = mean(corrkind,na.rm=T),
            tcorru = mean(corrunrel,na.rm=T)) %>%
  gather(key="aoi",value = "corr",c("tcorrptl","tcorrn","tcorrk","tcorru")) %>%
  mutate(aoi = factor(aoi, levels = c("tcorrptl","tcorrn","tcorrk","tcorru"))) %>%
  group_by(experiment,kindknower,samplegroup,aoi) %>%
  get_summary_stats(corr, type="mean_se")
```

```{r}
auxctime %>%
  filter(experiment == "Experiment 2") %>%
  filter(kindknower == 1) %>%
  ggplot(aes(x=samplegroup,y=mean,color=aoi)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_blank()) +
  geom_vline(xintercept = 30, size=.15, color="black") +
  geom_vline(xintercept = 240/390*130, size=.15, color="black") +
  geom_hline(yintercept = 0, size=.15, color="black") +
  geom_errorbar(aes(ymin = mean-se, ymax = mean+se),alpha=.25) +
  geom_line() +
  ylim(-.56,.56) +
  xlab("Time (seconds)") +
  scale_x_continuous(
    breaks = c(1,61/390*130,121/390*130,181/390*130,241/390*130,301/390*130,360/390*130),
                     labels = c("0","1", "2", "3", "4", "5","6")) +
  scale_colour_manual(values=cbp2)

setwd("~/Documents/GitHub/composition/plots/") # Set the path
ggsave("timee2.png", plot = last_plot(), width = 10, height = 8, units = c("cm"))
```

```{r}
auxctime %>%
  filter(experiment == "Experiment 3") %>%
  filter(kindknower == 1) %>%
  ggplot(aes(x=samplegroup,y=mean,color=aoi)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_blank()) +
  geom_vline(xintercept = 30, size=.15, color="black") +
  geom_vline(xintercept = 240/390*130, size=.15, color="black") +
  geom_hline(yintercept = 0, size=.15, color="black") +
  geom_errorbar(aes(ymin = mean-se, ymax = mean+se),alpha=.25) +
  geom_line() +
  ylim(-.56,.56) +
  xlab("Time (seconds)") +
  scale_x_continuous(
    breaks = c(1,61/390*130,121/390*130,181/390*130,241/390*130,301/390*130,360/390*130),
                     labels = c("0","1", "2", "3", "4", "5","6")) +
  scale_colour_manual(values=cbp2)

setwd("~/Documents/GitHub/composition/plots/") # Set the path
ggsave("timee3.png", plot = last_plot(), width = 10, height = 8, units = c("cm"))
```

# PLOTS REVIEW

## Raw looking times

```{r}
resultsrawcompose <- dcompose %>%
  group_by(experiment,ID,trial,phase,targetnumeral,attpretest,atttest,atttrial) %>%
  summarise(sumtg = sum(tghit,na.rm=T)*1000/60/1000,
            sumdtnum = sum(dtnumhit,na.rm=T)*1000/60/1000,
            sumdtkind = sum(dtkindhit,na.rm=T)*1000/60/1000,
            sumdtunrel = sum(dtkunrelatedhit,na.rm=T)*1000/60/1000,
            sumct = sum(centerhit,na.rm=T))%>%
  select(ID,trial,phase,targetnumeral,sumtg,sumdtnum,sumdtkind,sumdtunrel,
         attpretest,atttest,atttrial)
```

```{r}
# Combine w/ kind info
resultsrawcombined <- merge(resultsrawcompose,resultskindindm,by=c("experiment","ID"))
```

```{r}
aux <- resultsrawcombined %>%
  filter(kindknower == 1) %>%
  filter(atttrial == 1) %>%
  filter(experiment == "Experiment 2") %>%
  group_by(ID,phase,targetnumeral) %>%
  summarise(msumtg = mean(sumtg,na.rm=T),
            msumdtnum = mean(sumdtnum,na.rm=T),
            msumdtkind = mean(sumdtkind,na.rm=T),
            msumdtunrel = mean(sumdtunrel,na.rm=T),
            n()) %>%
  gather(key="aoi",value="value",c("msumtg","msumdtnum","msumdtkind","msumdtunrel")) %>%
  mutate(aoi = factor(aoi, levels = c("msumtg","msumdtnum","msumdtkind","msumdtunrel")))
```

```{r}
resultsrawcombined %>%
  filter(kindknower == 1) %>%
  filter(atttrial == 1) %>%
  filter(experiment == "Experiment 2") %>%
  group_by(ID,phase) %>%
  summarise(msumtg = mean(sumtg,na.rm=T),
            msumdtnum = mean(sumdtnum,na.rm=T),
            msumdtkind = mean(sumdtkind,na.rm=T),
            msumdtunrel = mean(sumdtunrel,na.rm=T),
            n()) %>%
  gather(key="aoi",value="value",c("msumtg","msumdtnum","msumdtkind","msumdtunrel")) %>%
  mutate(aoi = factor(aoi, levels = c("msumtg","msumdtnum","msumdtkind","msumdtunrel"))) %>%
  ggplot(aes(x = as.factor(phase), y = value, fill = aoi, color = aoi)) +
  theme_pubr() +
  theme(legend.position = "top") +
  geom_violin(data = aux, aes(x = phase, y = value, fill = targetnumeral),
              size = .15, alpha = .15) + 
  geom_jitter(position=position_jitterdodge(.25), size = .75, alpha = .85) +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point",
               color = "black", 
               size = 2, shape = "circle",position=position_dodge(width = .75)) +
  stat_summary(fun.data = mean_cl_normal, na.rm = TRUE,
               color = "black", 
               size = .5, position=position_dodge(width = .75),geom = "errorbar", width = 0) +
  scale_color_manual(values=cbp1) +
  scale_fill_manual(values=cbp1) +
  ylim(0,3.15) +
  labs(title = "Experiment 3", subtitle = "Raw looking times")

```



```{r}
setwd(pathplots) 
ggsave("rawe2.png", plot = last_plot(), width = 10, height = 10, units = c("cm"))
```



## corrpl

```{r}
resultscombinedindm %>%
  gather(key="aoi",value="value",c("mpretg","mprenum","mprekind","mpreun",
                                     "mtesttg","mtestnum","mtestkind","mtestun",
                                   "mcorrtg","mcorrnum","mcorrkind","mcorrun")) %>%
  select(experiment, ID, kindknower, aoi, value) %>%
  mutate(measure = case_when(
    str_detect(aoi, "pre") ~ "Pretest",
    str_detect(aoi, "test") ~ "Test",
    str_detect(aoi, "corr") ~ "Baseline corrected")) %>%
  mutate(measure = factor(measure, levels = c("Pretest","Test","Baseline corrected"))) %>%
  mutate(aoi = case_when(
    str_detect(aoi, "tg") ~ "Target",
    str_detect(aoi, "kind") ~ "Kind Distractor",
    str_detect(aoi, "num") ~ "Number Distractor",
    str_detect(aoi, "un") ~ "Unrelated/Mixed Distractor"
    )) %>%
  filter(kindknower == 1) %>%
  filter(experiment == "Experiment 3") %>%
  ggplot(aes(x=as.factor(aoi),y=value,fill=as.factor(aoi))) + #, linetype = measure
  theme_pubr() +
  theme(legend.position = "bottom",
        title = element_text(size = 16),
        #axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = .25, size = .15, lty = "longdash", color = "gray") +
  geom_hline(yintercept = 0, size = .15, lty = "longdash", color = "darkred") +
  geom_boxplot(aes(alpha = as.factor(measure)),outlier.shape = NA, width = 1, color="gray10",
              size =.35) +
  geom_jitter(aes(color = aoi, shape = measure),position=position_jitterdodge(.5), size = .75) +
  ylim(-.56,.56) +
  #ylab("Mean Baseline-Corrected Proportion of Looking") +
  stat_summary(aes(group = interaction(aoi, measure)), fun.y = mean, na.rm = TRUE,
               geom = "point", color = "black", 
               size = 2, shape = "diamond", position = position_dodge(width = 1)) +
  labs(title = "Experiment 2", subtitle = "Composition test") +
  scale_colour_manual(values=cbp1) +
  scale_fill_manual(values=cbp2) +
  scale_alpha_manual(values = c(0.15,0.35,75))
```

```{r}
resultscombinedindm %>%
  gather(key="aoi",value="measure",c("mpretg","mprenum","mprekind","mpreun")) %>%
  mutate(aoi = recode(aoi,"mcorrtg" = "aTG","mcorrkind" = "dtkind","mcorrnum" = "dtnum")) %>%
  filter(kindknower == 1) %>%
  filter(experiment == "Experiment 2") %>%
  ggplot(aes(x=as.factor(aoi),y=corr,fill=aoi)) +
  theme_pubr() +
  theme(legend.position = "none",
        title = element_text(size = 16),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  geom_hline(yintercept = 0.25, size = .5, lty = "longdash", color = "gray") +
  geom_boxplot(outlier.shape = NA, alpha = .5, width = .3, color="gray10",size =.35) +
  geom_jitter(aes(color = aoi),position=position_jitter(.15), size = .75) +
  ylim(0,1) +
  #ylab("Mean Baseline-Corrected Proportion of Looking") +
  stat_summary(fun.y = mean, na.rm = TRUE,
               geom = "point", color = "white", 
               size = 4, shape = "diamond") +
  labs(title = "Experiment 2", subtitle = "Composition test") +
  scale_colour_manual(values=cbp1) +
  scale_fill_manual(values=cbp1)
```

```{r}

```

# SAVE

```{r}
setwd("~/Documents/GitHub/composition/results/") # Set the path
save(resultsindm, file = "resultse2e3.RData")
```
